Untitled

### 2016-11-16 Code/Explore_unaggregate_data.Rmd
small change
merged suppressed and non suppressed data

dim(dat.both)
dat.both <- merge(dat.both, cod.dict, by = "COD2") #to add on COD_num and cod_cat
dim(dat.both)
```

```{r pull_alabama}
alabama.males <- dat.both %>% filter(State2 == "Alabama", Sex2 == "Male")

save(alabama.males, file = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/alabama_males_granular.Rdata")
```

>>>>

head(dat.both)

dat.both <- dat.both[dat.both$Age2 != "Unknown", ]

dat.both <- dat.both %>% mutate(stabbrs = factor(State, levels = c(0:50), 
                                      labels = c("AL", "AK", "AZ", "AR", "CA", "CO", "CT", "DE", "DC",
                                                 "FL", "GA", "HI", "ID", "IL", "IN", "IA", "KS", "KY", 
                                                 "LA", "ME", "MD", "MA", "MI", "MN", "MS", "MO", "MT", 
                                                 "NE", "NV", "NH", "NJ", "NM", "NY", "NC", "ND", "OH", 
                                                 "OK", "OR", "PA", "RI", "SC", "SD", "TN", "TX", "UT", 
                                                 "VT", "VA", "WA", "WV", "WI", "WY")))

dat.both$agegrp <- dat.both$Age 
dat.both$agegrp[dat.both$Age == 0]  <- 1

dim(dat.both)
dat.both <- merge(dat.both, cod.dict, by = "COD2") #to add on COD_num and cod_cat
dim(dat.both)

```

```{r for_merge}

years0610 <- dat.both[dat.both$Year3 >= 2006 & dat.both$Year3 <= 2010 & dat.both$agegrp > 1, ] 
#added the age restriction because don't want to deal with the differences in age definition right now

not.suppressed <- foreign::read.dta("/Users/corinneriddell/Dropbox/VitalStats/notsuppressed_0610.dta")

not.suppressed <- not.suppressed %>% 
  filter(agegrp > 1)

years0610 <- years0610 %>% rename(COD_full = COD2)

together <- merge(years0610, not.suppressed, by = c("stabbrs", "Year3", "Sex", "Race", "agegrp", "COD_full"))

```

```{r}
together <- together %>% mutate(diff_count = Count - death, 
                                diff_pop = Population - popestimate,
                                rel_diff_pop = (Population - popestimate)/Population)

prop.table(table(together$death[is.na(together$Count) == T]))

ggplot(together, aes(x = diff_count)) + geom_density()
summary(together$diff_count)

ggplot(together, aes(x = diff_pop)) + geom_density()
summary(together$diff_pop)

ggplot(together, aes(x = rel_diff_pop)) + geom_density()
summary(together$rel_diff_pop)

View(together[together$rel_diff_pop > 0.6, ])
```
From above we see that the death counts match exactly and when the original count is NA the non-suppressed count is between 1 and 9.
For some reason there is some discrpancy in the populational denominators. These do not match exactly and I don't know why.

Since we are interested in the effect of imputing the NAs and not the effect of the different denominators, we need to use the same denominators in the analysis.

```{r pull_alabama}
alabama.males <- together %>% filter(State2 == "Alabama", Sex2 == "Male") 
save(alabama.males, file = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/alabama_males_5plus_granular.Rdata")
```
